---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse   = TRUE,
  warning    = FALSE,
  message    = FALSE,
  comment    = "#>",
  fig.path   = "man/figures/",
  fig.retina = 3
)
```

# {maddTools}

<!-- badges: start -->

<!-- badges: end -->

Miscellaneous functions for the GWU course [EMSE 6035: Marketing Analytics for Design Decisions](https://madd.seas.gwu.edu/)

## Installation

The package can be installed from GitHub:

```r
# install.packages("remotes")
remotes::install_github("emse-madd-gwu/maddTools")
```

Load the package with:

```{r, eval=FALSE}
library(maddTools)
```

## Contents

This package contains the following functions:

* `ci()`: Get confidence intervals for a vector of numbers or for every column in a data frame of numeric columns.
* `ggtornado()`: Creates a "tornado" plot using the [{ggplot2}](https://ggplot2.tidyverse.org/) package.
* `mvrnorm()`: Simulate draws from a multivariate normal distribution (from the {MASS} package).
* `logitProbs()`: Computes logit fraction given a set of coefficients and alternatives.
* `rep_df()`: Repeats a data frame `n` times.

To view more details of any of the functions, run `?functionName()` in R, replacing 'functionName' with the name of the function.

## Author, Version, and License Information

- Author: *John Paul Helveston* https://www.jhelvy.com/
- Date First Written: *August, 25, 2021*
- License: [MIT](https://github.com/emse-madd-gwu/maddTools/blob/master/LICENSE.md)

## Citation Information

If you use this package for in a publication, I would greatly appreciate it if you cited it - you can get the citation by typing `citation("maddTools")` into R:

```{r}
citation("maddTools")
```
